## Different Options for Connecting to Qualtrics API with qToolkit
### (in order of preference)

The `qapi_connect` function attempts an API connection to Qualtrics with the necessary credentials (`org_id` and `api_key`). These credentials can be passed one of three ways to the `qapi_connect` function as follows:

### Add the `org_id` and `api_key` to your ~/.Rprofile file

This method is the *most preferred* as it keeps your credentials in one file that is never hardcoded in the analysis file, and doesn't add any cruft to your project folder like setting an auth file does.

To do this option, simply open up your ~/.Rprofile file (depending on your distribution, this path may differ), and place the following line anywhere:

```{r}
options(QAPI_ORG_ID  = "OrganizationId",
        QAPI_API_KEY = "abcdefghijklmnopqrstuvwxyz")
```

where `QAPI_ORG_ID` is your `org_id` and `QAPI_API_KEY` is your `api_key`.

In this case, one would only need to call `qapi_connect()` with no parameters as the script will load the credentials from ~/.Rprofile.

### Supply the `org_id` and `api_key` to an auth file in the same directory as your survey analysi script

This option is made available for those who may have different API keys depending on which organization they are running analysis for. 

To use this option, create the `auth_file` in the current working directory and add to it the same lines as you would add to your ~/.Rprofile file above, like so:

```{r}
options(QAPI_ORG_ID  = "OrganizationId",
        QAPI_API_KEY = "abcdefghijklmnopqrstuvwxyz")
```

Again, to load these credentials one would simply call `qapi_connect()` with no parameters and the script will load the credentials from the `auth_file`.

By default, the `auth_file` the script looks for is `.qapi_auth.R` in the current working directory, but this filename can also be specified as a parameter in the `qapi_connect()` call, as shown below:

```{r}
qapi_connect(auth_file = "~/.qapi_credentials.R")
```

### Supply the `org_id` and `api_key` in the `qapi_connect` string

This method is the *least preferred* as it hardcodes sensitive API information into survey analysis scripts. This should only be used for testing purposes, or if the `org_id` and `api_key` you want to use differs from that stored in `options()`

```{r}
qapi_connect(org_id = "OrganizationID",
             api_key = "abcdefghijklmnopqrstuvwxyz")

```
