## How to Connect to the Qualtrics API with qToolkit

The `qapi_connect` function attempts an API connection to Qualtrics with the 
necessary credentials (`org_id` and `api_key`). These credentials can be passed 
one of three ways to the `qapi_connect` function.

Please note that the first method shown below is the preferred method! The other 
two options are available to use if you need them.

### Add `org_id` and `api_key` to your ~/.Rprofile File

The `.Rprofile` file is a hidden file located in the home directory of your 
computer. If you add your qualtrics credentials to this file, then you can 
automagically connect to the qualtrics API and access all of your surveys, 
without having to pass additional information.

Modifying your `.Rprofile` file is *preferred* as it stores your credentials in a 
hidden file that you are not likely to push to github or drop box or some other 
more public facing api. 

To modify your .Rprofile file, 

1. open up your `~/.Rprofile` file (depending on your distribution, this path may differ). You may find using shell or bash to find the file is preferred. Then place the following code
into the file:

```{r}
options(QAPI_ORG_ID  = "OrganizationId",
        QAPI_API_KEY = "abcdefghijklmnopqrstuvwxyz")
```

where `QAPI_ORG_ID` is your `org_id` and `QAPI_API_KEY` is your `api_key`.

Once your credentials are stored in the `.Rprofile`, you can call  `qapi_connect()` 
with no parameters as the script will load the credentials from `~/.Rprofile`.

HINT:
TO find your .Rprofile file. Open terminal (on a mac) or gitbash on a pc. and cd
to your home directory.

```{shell}
# cd to your home directory
cd . 
# open r profile in your favorite text editor. below we use vim
vim .Rprofile 

```

### Add an Auth File To Your `R` Working Directory
 
Sometimes you may be using different qualtrics instances with different authentication
for different projects. In this case, you can add an auth_file to a working directory 
with unique credentials for that R working directory. 

To use this option, create the `auth_file` in the current working directory and 
add to it the same lines as you would add to your `~/.Rprofile` file above, like so:

```{r}
options(QAPI_ORG_ID  = "OrganizationId",
        QAPI_API_KEY = "abcdefghijklmnopqrstuvwxyz")
```

To load these credentials you call `qapi_connect()` with no parameters. The script 
will load the credentials from the `auth_file`.

By default, the `auth_file` the script looks for is `.qapi_auth.R` in the current 
working directory, but this filename can also be specified as a parameter in the 
`qapi_connect()` call, as shown below:

```{r}
qapi_connect(auth_file = "~/.qapi_credentials.R")
```

### Supply the `org_id` and `api_key` in the `qapi_connect` string

This method is the *least preferred* as it hardcodes sensitive API information 
into survey analysis scripts. This should only be used for testing purposes, 
or if the `org_id` and `api_key` you want to use differs from that stored in `options()`

```{r}
qapi_connect(org_id = "OrganizationID",
             api_key = "abcdefghijklmnopqrstuvwxyz")

```
