---
title: "Get Started Working with Survey Data: Matrix and Multiple Choice Questions"
author: "Leah Wasser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Get Started Working with Survey Data: Matrix and Multiple Choice Questions}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Getting Survey Data From Qualtrics

To begin accessing qualtrics data through `qtoolkit`, you need to have your API
key setup. The example below assumes that you
have your key setup in your `.Rprofile` file OR in an `.auth` file in your working directory.
Refer to the API connect vignette for more details on that!

```{r connect, message=FALSE}
#options(stringsAsFactors = FALSE)
library(qtoolkit)
# still working on only importing the pipe element in the package.
# https://github.com/sckott/analogsea/issues/32
# note currently i need to just load the pipe and also stringsasfactors as false
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r eval = FALSE}
## Connect to Qualtrics API
qapi_connect()
```

Once you have connected to the api, you can quickly view all of the surveys that
you have access to through that API key. These are the same surveys you would see
when you login to your Qualtrics account.

```{r view-survey-list}
# get a list of all surveys connected to your account / api token
all_surveys <- list_surveys()
head(all_surveys)

```

The first column in the output data.frame from the `list_surveys()` function is
the survey ID for each survey. You can use that ID to grab the survey that you'd
like.

Note - there is also some functionality built in to grab that by name but that
is still in beta. The output of `qsurvey()` is a `qsurvey` object. this object
contains both the question and response data and metadata all together in one
happy place.

```{r get-survey}
# define survey id variable, then get survey object
survey_id <- "SV_1SUpa4C4UGkZnWB"
# note the warnings are OK. it's just a reminder to me that some questions are not
# processed "custom" i can turn these off once i'm confident that things work
# across all question types!
my_survey_ob <- qsurvey(survey_id)
```

Be forewarned that this will take a minute to populate as it needs to:

1. Hit the qualtrics API,
2. access the survey and
3. populate the object with all of the data.

IMPORTANT: you must have internet access for this step to work properly as it
is hitting another server to get your survey data!

Once this step is successful, the real fun can begin.

## View Survey Questions

Next, let's explore the survey data information returned from qtoolkit.
First, check out all of the questions in the survey. The returned object here
contains the question id, name and order. Pay close attention to the `qid` which is
DIFFERENT from the name. The name is what you see in Qualtrics. The problem with
the name is that you can have 2 questions with the same name in Qualtrics. You
can manually edit the name in qualtrics.

This is problematic.

Thus, when you get a question in `qtoolkit`, you will use the `qid` NOT the name
that you see (and can change) in Qualtrics.

To view a nice data.frame of all questions available in your survey, you can access
it via the `qsurvey` object as follows:

```{r view-all-questions}
# view all questions
my_survey_ob$questionList

```

Note that here, qtoolkit by default cleans up any manually formatting in your questions.
Manually formatting will appear as html. If you want to keep the html, simply set
string_html to FALSE.

```{r}
my_survey_ob <- qsurvey(survey_id,
                        clean_html = FALSE)
# view all questions
my_survey_ob$questionList
```

Notice now your questions contain any html formatting used to render your questions!

```{r}
my_survey_ob <- qsurvey(survey_id,
                        clean_html = TRUE)
# view all questions
all_questions <- my_survey_ob$questionList
all_questions
```

## Qsurvey Object Structure

Let's first break down how the `qsurvey` object is organized. Each question can
be found in the `questions$qidhere` slot of the object. AGAIN note that the
qid is the UNIQUE ID that qualtrics provides each question. The name is something
that you can change so don't use that!

If you want to get all of the data for a question with id `QID71`, you can use:

```{r}
# get responses and question information for qid71.
q4 <- my_survey_ob$questions$QID4
str(q4)
```

```{r}
# get responses and question information for qid71.
my_survey_ob$questions$QID4$choices
```

```{r}
# get responses and question information for qid71.
my_survey_ob$questions$QID4$responses

```

```{r}
# get responses and question information for qid71.
my_survey_ob$questions$QID4$subquestions
```

```{r}
# here, we just grab a df that has the data stacked in a way that is easily plottable
question_responses <- get_question_resp(q4)
head(question_responses)
```

Now you can plot! Let's pretend we just want a plain old bar plot of
responses

```{r}

# it could be nice to calculate a percentage to with some function or argument
question_responses %>%
  group_by(quest_text, choice_text) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  labs(title = "How Often You Use a Tool",
       x = "Frequency of Use",
       y = "Count")

```

Now create a plot with facets for each sub question in your question matrix.

```{r}
# it could be nice to calculate a percentage to with some function or argument
question_responses %>%
  group_by(quest_text, choice_text) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~quest_text, ncol = 2) +
  labs(title = "How Often You Use a Tool",
       x = "Frequency of Use",
       y = "Count")

```

Finally you may want to clean up the plot. Issues with this plot include:

1. it's hard to read text on the x axis as the text is too long and
2. the choices are not in the correct order

You can use the `choice_wrap` and `choice_factor` to fix this.

1. Set `choice_factor` to TRUE to ensure that the answers are a factor (an ordered
element that is most often a category). In this case we are plotting using a scale so there is an order associated with the responses.
2. `choice_wrap`: This argument allows you to wrap the choice responses. Select a number (an integer) which will represent the number of characters to insert a line break. So if you set it to 8, you will get a line break every 8 characters.

Note that `\n` represents a line break in `R`.

```{r}

question_responses <- get_question_resp(q4,
                                        quest_wrap = NULL,
                                        choice_wrap = 8,
                                        choice_factor = TRUE)
head(question_responses)

question_responses %>%
  group_by(quest_text, choice_text) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~quest_text, ncol = 2) +
  labs(title = "How Often You Use a Tool",
       x = "Frequency of Use",
       y = "Count")
```

The above looks a lot nicer. However, now we may want to flip the order of our
likert scale for plotting. You can do that using the argument `choice_rev`
which accepts a boolean TRUE or FALSE.

```{r}
question_responses <- get_question_resp(q4,
                                        quest_wrap = NULL,
                                        choice_wrap = 8,
                                        choice_factor = TRUE,
                                        choice_rev = TRUE)
head(question_responses)

question_responses %>%
  group_by(quest_text, choice_text) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~quest_text, ncol = 2) +
  labs(title = "How Often You Use a Tool",
       x = "Frequency of Use",
       y = "Count")
```
