---
title: "Side by Side Matrices in QToolkit"
author: "Leah Wasser"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Side by Side Matrices in QToolkit}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Survey Question Types

So you've gotten the API all setup and now you need to plot data from different
types of questions. In this vignette, we will focus on the matrix and side-by-side (SBS)
matrix type.

NOTE: it's not recommended to use SBS matrices given the high cognitave load.
It makes taking a survey harder for your participants. With that said, we used
them ourselves before knowing better and want to ensure things don't break
on any survey that you process! So support is provided here to work with them!

To begin load all of the libraries
```{r connect, message=FALSE}
library(qtoolkit)
library(ggplot2)
library(dplyr)
library(tidyr)
```

Connect to the API if you haven't already!

```{r eval = FALSE}
## Connect to Qualtrics API
qapi_connect()
```

And select a survey.

```{r view-survey-list}
# get a list of all surveys connected to your account / api token
all_surveys <- list_surveys()
# define survey id variable, then get survey object
survey_id <- "SV_1SUpa4C4UGkZnWB"
my_survey_ob <- qsurvey(survey_id,
                        clean_html = TRUE)
# view all questions
all_questions <- my_survey_ob$questionList
all_questions
```

Let's work with QID54 which is a side-by-side matrix.
SBS matrices are more complex objects because it is several matrices that appear
next to each other in a survey.

```{r}
# get responses and question information for qid71.
q54_obj <- my_survey_ob$questions$QID54
str(q54_obj)
```

Notice here the choices in the SBS matrix are all the same! this makes analysis easy
although this type of question is still hard for your participants to take!

```{r}
# get responses and question information for qid71.
my_survey_ob$questions$QID54$choices
```

Note below that the matrix question type has more complex column headers. This
structure represents the question number `Q46`, the column number or matrix number `1`
and then the sub question number `_3`.

So

`Q46.1_1`

represents question 46 (as labeled in your survey) which has the unique id QID54 in qualtrics.
.1 represents matrix number one in a side by side matrix and _1 represents the first
question in that matrix.

```{r}
# get responses and question information for qid71.
my_survey_ob$questions$QID54$responses

```

Here are the sub questions in each matrix. Lucky for us all subquestions are
always the same in a qualtrics SBS question type.

```{r}
# get responses and question information for qid71.
my_survey_ob$questions$QID54$subquestions
```

```{r}
# here, we just grab a df that has the data stacked in a way that is easily plottable
q54 <- get_question_resp(q54_obj)
head(q54)
```

Now you can plot! Below we plot responses for each matrix in it's own ggplot facet.

```{r, fig.height=6, fig.width = 8}

# it could be nice to calculate a percentage to with some function or argument
q54 %>%
  group_by(quest_text, choice_text, matrix_num) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~matrix_num, nrow = 2) +
  labs(title = "How Often You Use a Tool",
       x = "Frequency of Use",
       y = "Count")

```

Now create a plot with facets for each sub question in your question matrix.

** note that choice_rev isn't working yet.

```{r, fig.height=6, fig.width = 8}

# here, we just grab a df that has the data stacked in a way that is easily plottable
q54 <- get_question_resp(q54_obj,
                         choice_factor = TRUE, choice_rev = TRUE)
# it could be nice to calculate a percentage to with some function or argument
q54 %>%
  group_by(quest_text, choice_text, matrix_num) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~matrix_num, nrow = 2) +
  labs(title = "How Often You Use a Tool\n Factors turned on",
       x = "Frequency of Use",
       y = "Count")

```

Next, let's explore a SBS matrix where the answer options are different.
First, we import and plot the data with factors set to `FALSE` (the default option).

```{r, fig.height=6, fig.width = 8}

# here, we just grab a df that has the data stacked in a way that is easily plottable
q55 <- get_question_resp(my_survey_ob$questions$QID55)
# it could be nice to calculate a percentage to with some function or argument
q55 %>%
  group_by(quest_text, choice_text, matrix_num) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  facet_wrap(~matrix_num, nrow = 2) +
  labs(title = "How Often You Use a Tool\n Factors turned on",
       x = "Frequency of Use",
       y = "Count")

```

If you turn factors ON then it will return a list of data.frames - one data frame
for each col in a SBS matrix.

```{r, fig.height=6, fig.width = 8}

# here, we just grab a df that has the data stacked in a way that is easily plottable
q55 <- get_question_resp(my_survey_ob$questions$QID55,
                         choice_factor = TRUE)
# it could be nice to calculate a percentage to with some function or argument
q55[[1]] %>%
  group_by(quest_text, choice_text) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  labs(title = "How Often You Use a Tool\n Factors turned on",
       x = "Frequency of Use",
       y = "Count")

```

Switch the order of the factor options using choice_rev.

```{r, fig.height=6, fig.width = 8}

# here, we just grab a df that has the data stacked in a way that is easily plottable
q55 <- get_question_resp(my_survey_ob$questions$QID55,
                         choice_factor = TRUE,
                         choice_rev = TRUE)
# it could be nice to calculate a percentage to with some function or argument
q55[[1]] %>%
  group_by(quest_text, choice_text) %>%
  count() %>%
  ggplot(aes(x = choice_text, y = n)) +
  geom_bar(stat = "identity") +
  labs(title = "How Often You Use a Tool\n Factors turned on",
       x = "Frequency of Use",
       y = "Count")

```

In this example, you can't use factors AND plot all matrices in one pretty plot.
